Reviewer comments from PeerJ

### 2015-03-05 PeerJResponse.tex
Edits
response to review; reviewer 2
Edits
Edits to last of reviewer 2 comments regarding greenhouse vs. field

\lev{Sure greenhouse is different than outside, but we can't control for variation outside whereas we can in a greenhouse. I don't understand their point. Greenhouse is best we could do here since they wouldn't all fit in a growth chamber.}

\mbh{I'd point out that the effect of \emph{tb1} on tillering has been verified a number of times in a number of environments (probably in a greenhouse setting) and cite studies like Briggs, etc...}

>>>>

\res{The effects of \emph{tb1} on tillering in maize have been verified a number of times in different environments \citet{Briggs2007, Clark2006, StuderDoebley2012, Studer2011}. We feel that any effect of growing teosinte in a greenhouse setting as opposed to as a field trial would not be so large as to mask the effects of \emph{tb1} on tillering.}
